\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} -- \small#3 & \small #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sam Guyette} \\ \vspace{1pt}
    \small (310) 403-2814 $|$ \href{mailto:samguyette@gmail.com}{\underline{samguyette@gmail.com}} $|$
    \href{https://www.samguyette.com}{\underline{www.samguyette.com}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cash App (Block)}{Jan 2026 -- Mar 2026 (Impacted by 50\% company-wide layoff)}
      {Software Engineer}{}
      \resumeItemListStart
        \resumeItem{Implemented a cross-service payment claiming feature enabling users to send money to recipients without Cash App accounts, coordinating workflows across multiple backend services using event-driven architecture.}
        \resumeItem{Developed APIs, Kafka consumers, and DynamoDB indexing to support asynchronous payment resolution, shipping the feature end-to-end in six weeks.}
        \resumeItem{Contributed to an early-stage AI code review tool in Rust and Svelte, making PR reviews faster and more efficient in an AI-native world.}
      \resumeItemListEnd

    \resumeSubheading
      {System1}{Aug 2025 -- Dec 2025}
      {Software Engineer}{}
      \resumeItemListStart
        \resumeItem{Built an automated ad campaign platform that generated and deployed GenAI creatives (images, titles, descriptions) across multiple ad networks, scaling to 10K+ campaign launches per day.}
        \resumeItem{Designed and implemented integration layers for Google and MediaGo that translated real-time creative inputs into network-specific campaign payloads, enabling fully automated multi-network campaign launches.}
        \resumeItem{Led a company-wide Tech All Hands, presenting “Why Context Matters”. Introducing intentional context compaction alongside a three-phase framework (Research, Planning, Implementation) to reduce hallucinations and improve LLM-assisted code quality.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon}{Aug 2022 -- Mar 2025}
      {Software Development Engineer}{}
      \resumeItemListStart
        \resumeItem{Designed, built, and maintained systems to protect Amazon's worldwide businesses from payment-related fraud, misuse, and abuse. These systems serve 25,000 transactions per second, while ensuring high availability, throughput, and low latency.}
        \resumeItem{Led the integration of the Discover payment network into Amazon's internal chargeback workflow, automating over 500 daily manual investigations, improving operational efficiency.}
        \resumeItem{Designed and implemented a monitoring application for entry gate metrics at Amazon Go and Whole Foods stores, delivering real-time alerts to machine learning scientists. The system identifies unintended abnormalities caused by fraud model changes, such as major customer blockages, enabling fast rollbacks within minutes instead of hours.}
        \resumeItem{Led Prime Day preparation for a critical microservice essential for processing Amazon.com orders. This involved calculating host requirements, setting throttling limits, running stress and chaos tests, and monitoring performance metrics to guarantee service availability during high traffic periods.}
      \resumeItemListEnd

    \resumeSubheading
      {Amount}{Apr 2021 -- Aug 2022}
      {Software Engineer}{}
      \resumeItemListStart
        \resumeItem{Developed point-of-sale financing solutions for major financial institutions, including Capital One, Guaranteed Rate, and Barclays as part of the Partner Implementation Team.}
        \resumeItem{Implemented risk assessment modules for digital identity, income verification, bank account validation, and employment checks.}
        \resumeItem{Refactored core platform code to adopt modern design patterns, improving scalability to support an expanding portfolio of banking partners.}
      \resumeItemListEnd

    \resumeSubheading
      {Epson}{Jun 2018 -- Sep 2018, Jun 2019 -- Sep 2019}
      {Software Engineer Intern}{}
      \resumeItemListStart
        \resumeItem{Designed and implemented automated market monitoring tools that scraped third-party resellers to ensure compliance.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd\vspace{-28pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Santa Cruz}{Sep 2016 -- Jun 2020}
      {Bachelor of Science, Computer Science}{}
  \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Additional}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Kotlin, Python, Java, JavaScript (React, Next, Node), Ruby/Rails} \\[4pt]
     \textbf{Cloud \& DevOps}{: AWS (ECS, DynamoDB, S3, Lambda, SQS, SNS, IAM, Route 53, CloudWatch, CloudFormation, and more), Infrastructure-as-Code, CI/CD, Monitoring and Alerting} \\[4pt]
     \textbf{Development}{: Microservice Architecture, Distributed Systems, Hexagonal Architecture, AI-Assisted Development, Unit and Integration Testing, A/B Testing} \\[4pt]
     \textbf{Awards}{: 2024 IPAT on the Back Recipient (Amazon) -- Recognized for driving platform adoption across the organization.}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}